\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}

\title{Seminar 6}
\author{Octavian Custura }
\date{January 2021}

\begin{document}

\maketitle

\textbf{8. } Two independent customers are scheduled to arrive in the afternoon. Their arrival times are uniformly distributed between 2 pm and 8 pm. What is the expected time of \\
a) the first (earlier) arrival; \\
b) the last (later) arrival? \\

\begin{proof}
We need to compute the expectations of min and max functions.
Let $Z = max(X, Y)$ and $U = min(X, Y)$

The cdf of max is \[F_Z(z) = P(Z \leq z) = P(X \leq z, Y \leq z) = P(X \leq z)P(Y \leq z) = (\frac{z - 2}{8 - 2})^2\]
Thus, the pdf is $f_Z(z) = \dfrac{z-2}{18}$.
The cdf of min is 
\begin{equation*}
    \begin{split}
        F_U(u) = P(U \leq u) &= 1 - P(U \geq u) \\ &= P(X \geq u)P(Y \geq u) \\ &= 1 - (1 - \frac{u - 2}{6})^2 \\ &= 1 - ({\frac{8 - u}{6}})^{2}
    \end{split}
\end{equation*}
The pdf is $f_U(u) = \dfrac{8-u}{18}$.

Finally, we need to compute $E(Z)$ and $E(U)$.
\[ E(U) = \int_{2}^{8} u \dfrac{8 - u}{18} \, du = 4 pm, \text{earliest arrival} \]
\[ E(Z) = \int_{2}^{8} z \dfrac{z-2}{18}\, dz = 6 pm, \text{latest arrival}\]

\end{proof}
\textbf{9.}  In an office n different letters are placed randomly into n addressed envelopes. Let $Z_n$ denote the number of
correct mailings. For each $k \in \{1, . . . , n\}.$, let $X_k$ be the random variable defined by
$$
X_k = \begin{cases} 1 \text{, if the k-th letter is placed correctly} \\
0, \text{, otherwise.}\end{cases}$$ \\
a) Find $E(X_k)$ and $V (X_k)$ for each $k \in \{1, . . . , n\}.$ \\
b) Find $E(Z_n)$ and $V(Z_n)$.\\
c) How many correct mailings are to be expected? \\

\begin{proof}
a, b) We know that $X = X_1 + X_2 + X_3 + ... + X_n$, thus $E(X) = E(X_1) + E(X_2) + ... + E(X_n)$

We need to compute $E(X_k)$, for $k \in \{1, . . . , n\}.$ Since all possibilities of mailing are equally possible, $E(X_k) = E(X_1).$
Since $X_1$ is a variable with values 0 or 1, then $E(X_1) = P(X_1 = 1) = \frac{1}{n}$
\[
    E(Z_n) = E(X_1) + E(X_2) + ... + E(X_n) = n \cdot \frac{1}{n} = 1
\]
 \[ Z_n^2 = \sum_{i=1}^{n}{X_i^2} + \sum_{(i,j) = (1, 1), i \neq j}^{(n, n)}{X_i X_j}\]


We need to compute $E(X_k^2) = E(X_1^2) = E(X_1) = \frac{1}{n}$, since the pdf of $X_1^2$ is 
\begin{equation*}
    \begin{pmatrix}
    0 & 1 \\
    \frac{n - 1}{n} & \frac{1}{n}
    \end{pmatrix}
\end{equation*}

\begin{equation*}
    \begin{split}
    E(X_k X_p) &= E(X_1 X_2) = P(X_1 X_2 = 1) \\ &= P(X_1 = 1, X_2 = 1) = P(X_1 = 1) P(X_2 = 1 | X_1 = 1) = \frac{1}{n} \cdot \frac{1}{n - 1}
    \end{split}
\end{equation*}
\begin{equation*}
\begin{split}
     E(Z_n^2) &= \sum_{i=1}^{n}{E(X_i^2)} + \sum_{(i,j) = (1, 1), i \neq j}^{(n, n)}{E(X_i X_j)} \\
     &= n \cdot \frac{1}{n} + n\cdot (n - 1) \cdot \frac{1}{n} \cdot \frac{1}{n - 1} \\
     &= 2
\end{split}
   
\end{equation*}
\begin{equation*}
    V(X_k) = E(X_k^2) - (E(X_k))^2 = \frac{1}{n} - \frac{1}{n^2} = \frac{n - 1}{n^2}
\end{equation*}
\begin{equation*}
    V(Z_n) = E(Z_n^2) - (E(Z_n))^2 = 2 - 1 = 1
\end{equation*}

c) There are to be expected $E(Z_n) = 1$ correct mailing.
\end{proof}
\end{document}
